%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.pedrotammela.com}{\Large Pedro Caldas Tammela}} & Email : \href{mailto:pctammela@gmail.com}{pctammela@gmail.com}\\
  \href{https://www.pedrotammela.com/}{https://www.pedrotammela.com} & Mobile : +55-21-99866-5009 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Pontifícia Universidade Católica do Rio de Janeiro}{Rio de Janeiro, Brazil}
      {Bachelor of Computer Science}{Jan. 2015 -- Dec. 2019}
      \resumeItemListStart
      \resumeItem{{Bachelor's Thesis}}
          {Scripting Linux system calls with Lua.}
      \resumeItem{{Awarded}}
          {90\% Scholarship for 3 years.}
       \resumeItem{{Course Emphasis}}
          {Programming languages theory and Distributed systems}
      \resumeItemListEnd
    \resumeSubheading
      {Pontifícia Universidade Católica do Rio de Janeiro}{Rio de Janeiro, Brazil}
      {Minor in Entrepreneurship}{Jul. 2017 -- Dec. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://www.cujo.com}{CUJO AI}}{Rio de Janeiro, Brazil}
      {Contractor}{Jan. 2017 - Present}
      \resumeItemListStart
      \resumeItem{{Cross architecture development}}
          {ARM, x86 and MIPS architectures.}
      \resumeItem{\href{https://github.com/luainkernel/lunatik}{Lunatik}}
          {A porting project of the Lua scripting language to the Linux kernel.}
      \resumeItem{\href{https://www.pedrotammela.com/slides/nflua-luaw17.pdf}{NFLua}}
          {A packet scripting engine based on Lunatik and Netfilter.}
      \resumeItem{{Meta-data parsing}}
          {Protocols parser written in Lua for software interrupt processing.}
      \resumeItem{{Packet meta-data analysis}}
          {Layer 3/4 meta-data analysis and real time data collection.}
      \resumeItem{{Layer 3 quarantine}}
          {A layer 3 packet quarantine using skb references.}
      \resumeItem{{Packet reputation}}
          {Real time packet reputation analysis with distributed communication and kernel/user-space synchronization.}
      \resumeItem{{Proof of Concepts}}
          {Written numerous proof of concepts in Lua and C for upcoming features, researching the feasibility of the feature in an embedded platform with limited resources.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Certifications-----------------
\section{Certifications}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://summerofcode.withgoogle.com}{Google Summer of Code}}{Rio de Janeiro, Brazil}
      {Associate Mentor for LabLua}{May 2018 - Aug. 2018}
      \resumeItemListStart
      \resumeItem{\href{https://github.com/caioluiz/lunatik}{Rcu for Lunatik}}
          {A Lua binding for the kernel Rcu API. Developed by Caio Messias.}
      \resumeItem{\href{https://github.com/tcz717/lunatik/tree/luasocket-with-docs/socket}{Socket for Lunatik}}
          {A Lua binding for the kernel Socket API. Developed by Chengzhi Tan.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
 %-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \item{
        \href{https://github.com/tammela/lua-llvm-binding}{\textbf{Lua LLVM Binding}}{: A Lua binding for the C LLVM Backend.}
    }
    \item{
        \href{https://github.com/luainkernel}{\textbf{Lua in Kernel}}{: Continuous development and support for kernel ports of the Lua scripting language.}
    }
    \item{
        \href{https://github.com/luainkernel/lunatik}{\textbf{Lunatik}}{: A port of the Lua language for the x86 Linux kernel. Originally developed by CUJO AI.}
    }
    \item{
        \href{https://github.com/luainkernel/poc-driver}{\textbf{PoC Driver}}{: A driver that provides a pseudo device to run Lua scripts inside the kernel. Written for proof of concepts.}
    }
    \item{
        \href{https://www.pedrotammela.com}{\textbf{Personal Website}}{: Where I write about interesting stuff.}
    }

  \resumeSubHeadingListEnd

 %-----------Conferences-----------------
\section{Conferences}
  \resumeSubHeadingListStart
    \item{
        \textbf{Google Summer of Code 2018}{: Conference sponsored by Google for GSoC Mentors in Sunnyvale, California.}
    }
    \item{
        \textbf{Lua Workshop 2018 (Speaker)}{: Conference sponsored by CUJO AI in Kaunas, Lithuania.}
    }
    \item{
        \textbf{Lua Workshop 2017}{: Conference sponsored by KONG in San Francisco, California.}
    }
    \item{
        \textbf{LuaConf 2017}{: Conference sponsored by PUC-Rio in Rio de Janeiro, Brazil.}
    }
    \item{
        \textbf{LuaConf 2016}{: Conference sponsored by PUC-Rio in Rio de Janeiro, Brazil.}
    }
  \resumeSubHeadingListEnd
\end{document}
